---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# snomed: An R data package containing SNOMED code usage counts in Primary Care in England

<!-- badges: start -->

<!-- badges: end -->

The goal of `snomed` is to to make anonymous SNOMED code usage counts in Primary Care in England available in R. 
The original data is available from NHS Digital at <https://digital.nhs.uk/data-and-information/publications/statistical/mi-snomed-code-usage-in-primary-care>.

## Installation

You can install the development version of `snomed` like so:

```r
remotes::install_github("milanwiedemann/snomed")
```

## Example

```{r load-pkg}
# Load snomed package
library(snomed)
```
### SNOMED Code Usage in Primary Care in England

```{r data-usage}
# Return snomed code usage data
snomed_usage
```

### Dictionary of SNOMED Code Descriptions in Primary Care in England

```{r data-dict}
# Return snomed code dictionary
snomed_dict
```

