---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clinicalActivity: Clinical Activity in England 

<!-- badges: start -->

<!-- badges: end -->

The goal of `clinicalActivity` is to make yearly summaries of **SNOMED Code Usage in Primary Care** and **Hospital Admitted Patient Care Activity** published by NHS Digital available in R for research. 
The original data is available from NHS Digital at:

- [SNOMED Code Usage in Primary Care](https://digital.nhs.uk/data-and-information/publications/statistical/mi-snomed-code-usage-in-primary-care)
- [Hospital Admitted Patient Care Activity](https://digital.nhs.uk/data-and-information/publications/statistical/hospital-admitted-patient-care-activity)

## Installation

You can install the development version of `clinicalActivity` like so:

```r
remotes::install_github("milanwiedemann/clinicalActivity")
```

## Example

```{r load-pkg}
# Load clinicalActivity package
library(clinicalActivity)
```

### SNOMED Code Usage in Primary Care in England

```{r snomed-usage}
# Return SNOMED code usage data
snomed_usage
```

### Hospital Admitted Patient Care Activity

```{r icd10-usage}
# Return ICD-10 code usage data
icd10_usage
```

